A Bidirected String Graph Model of Genome Assembly

### 2012-11-28 presentation/presentation.tex
Suggestions

@@

@@

\begin{frame}{Overlaps between reads}
	Consider two reads, $f$ and $g$, and their reverse complements $f'$ and $g'$.
	The reads $f$ and $g$ are said to {\bf exactly overlap} by some length
	$\ell$ iff at least one of the following is true:
	\begin{itemize}
		\item The last $\ell$ bp of $f$ exactly match the first $\ell$ bp of
		$g$.
		\item The last $\ell$ bp of $f$ exactly match the first $\ell$ bp of
		$g'$.
		\item The last $\ell$ bp of $f'$ exactly match the first $\ell$ bp of
		$g$.
		\item The last $\ell$ bp of $f'$ exactly match the first $\ell$ bp of
		$g'$.
	\end{itemize}
	An exact overlap $o$ is fully described by the tuple $(f, g, f_{beg},
	g_{beg}, len, rc)$.
	%there $f$ and $g$ are the reads of the overlap,
	%$f_{beg}$ and $g_{beg}$ and the starting position of the overlap on each
	%read, $len$ is the length of the overlap, and $rc$ indicates whether the
	%overlap is reverse-complement or not.
\end{frame}

@@

\begin{frame}{Three types of overlaps}
	\begin{enumerate}
		\item ``Normal'' overlap
			\begin{center}
				\begin{tikzpicture}
					\draw[->,style=thick] (0,0) -- (2,0);
					\draw[->,style=thick] (1.0,0.3) -- (3.0,0.3);
				\end{tikzpicture}

@@

				\begin{tikzpicture}
					\draw[->,style=thick] (2,0) -- (0,0);
					\draw[->,style=thick] (3.0,0.3) -- (1.0,0.3);
				\end{tikzpicture}
			\end{center}
		\item ``Innie'' overlap
			\begin{center} \begin{tikzpicture}
					\draw[->,style=thick] (0,0) -- (2,0);
					\draw[->,style=thick] (3,0.3) -- (1,0.3);
			\end{tikzpicture} \end{center}
		\item ``Outtie'' overlap
			\begin{center} \begin{tikzpicture}
					\draw[->,style=thick] (2,0) -- (0,0);
					\draw[->,style=thick] (1.0,0.3) -- (3.0,0.3);
			\end{tikzpicture} \end{center}
	\end{enumerate}
\end{frame}

\begin{frame}{Computing overlaps}
	\begin{itemize}
		\item Goal: compute all pairwise overlaps of some minimum length $\ell$
		among the reads.
		\item Naive algorithm compares every read with every other read ($N$
		reads: $N^2$ time)
		\item A faster algorithm indexes the reads by short subsequences, then
		only compares reads that share a subsequence ("seed-and-extend").
		\item Overlaps may be exact, or they may allow for differences up to a
		certain threshold.
	\end{itemize}
\end{frame}

\begin{frame}{Computing overlaps (Implementation)}
	\begin{itemize}
		\item Implementation: {\tt compute-overlaps}
			\begin{itemize}
				\item {\bf Input}:  A set of reads and the minimum overlap
				length $\ell$
				\item {\bf Output}:  All exact pairwise overlaps between reads,
				including reverse-complement overlaps
				\item {\bf Algorithm}:  Seed-and-extend
				\item {\bf Running time}: Linear with respect to genome length
				for non-repetitive genomes; quadratic with respect to read
					density; quadratic with respect to the number of times a
					sequence of DNA is repeated in the genome
			\end{itemize}
	\end{itemize}
	%\begin{algorithm}[H]
		%\caption{Algorithm {\sc compute-overlaps}($S$)}
		%\begin{algorithmic}
			%%\STATE{h = new hash table}
			%%\FOR{{\bf each} read $r \in S$}
				%%\FOR{{\bf each} canonical $k$-mer $K \in R$}
					%%\STATE{Append $K.pos$ to $h[K]$}
				%%\ENDFOR
			%%\ENDFOR
			%%\FORALL{posList $\in h$}
				%%\FORALL{$k$-mer pairs $k1$, $k2$ in 
			%%\ENDFOR
		%\end{algorithmic}
	%\end{algorithm}
\end{frame}

@@

		\begin{center}
			\begin{tikzpicture}
				\draw[->,style=thick] (0,0) -- (2,0);
				\draw[->,style=thick] (3,0.3) -- (1,0.3);
			\end{tikzpicture}
			\hspace{5mm}or\hspace{5mm}
			\begin{tikzpicture}
				\draw[->,style=thick] (0,0.3) -- (2,0.3);
				\draw[->,style=thick] (3, 0) -- (1, 0);
			\end{tikzpicture}
			\hspace{5mm} ?
		\end{center}

@@

		\begin{center}
			\begin{tabular}{p{1cm}cccc}
				{\footnotesize Overlap} &
				\begin{tikzpicture}[scale=0.6]
						\draw[->,style=thick] (2,0) -- (0,0);
						\draw[->,style=thick] (1,0.3) -- (3,0.3);
				\end{tikzpicture} 
				& 
				\begin{tikzpicture}[scale=0.6]
						\draw[->,style=thick] (0,0) -- (2,0);
						\draw[->,style=thick] (3,0.3) -- (1,0.3);
				\end{tikzpicture} 
				& 
				\begin{tikzpicture}[scale=0.6]
						\draw[->,style=thick] (0,0) -- (2,0);
						\draw[->,style=thick] (1,0.3) -- (3,0.3);
				\end{tikzpicture} 
				&
				\begin{tikzpicture}[scale=0.6]
						\draw[->,style=thick] (2,0) -- (0,0);
						\draw[->,style=thick] (3,0.3) -- (1,0.3);
				\end{tikzpicture} 
				\\
				&$\downarrow$ & $\downarrow$& $\downarrow$& $\downarrow$ \\
				{\footnotesize Bidirected edge} &
				\begin{tikzpicture}[scale=0.6,>=triangle 45]
						\draw[<->,style=thick] (0,0) -- (2,0);
				\end{tikzpicture} 
				& 
				\begin{tikzpicture}[scale=0.6,>=triangle 45]
						\draw[>-<,style=thick] (0,0) -- (2,0);
				\end{tikzpicture} 
				& 
				\begin{tikzpicture}[scale=0.6,>=triangle 45]
						\draw[>->,style=thick] (0,0) -- (2,0);
				\end{tikzpicture} 
				&
				\begin{tikzpicture}[scale=0.6,>=triangle 45]
						\draw[<-<,style=thick] (0,0) -- (2,0);
				\end{tikzpicture} 
			\end{tabular}
		\end{center}

@@

\begin{frame}{Walks in a bidirected graph}
	\begin{itemize}
		\item A {\bf walk in a bidirected graph} $G$ is a continuous sequence of
		edges in $G$ such that if any vertex $v$ is entered through a head
		inwards, it is left on a head outwards (unless it is the end of the
		path), and vice versa.
		\item A bidirected edge may be traversed in opposite directions during
		the same walk.
		\item The reverse of a walk in a directed graph is also a bidirected walk.
		\item $1 \to 2 \to 3 \to 4$ and $4 \to 3 \to 2 \to 1$ are both valid
		walks in the bidirected graph below.
	\end{itemize}
		\begin{center} {\small
		\begin{tikzpicture}[>=triangle 45]
			\tikzstyle{every node} = [circle,fill=blue!20,draw=black];
			\node (1) at (0.00, 0) {1};
			\node (2) at (1.75, 0) {2};
			\node (3) at (3.50, 0) {3};
			\node (4) at (5.25, 0) {4};
			\draw[<->,very thick] (1) edge (2);
			\draw[>-<,very thick] (2) edge (3);
			\draw[<-<,very thick] (3) edge (4);
		\end{tikzpicture} } \end{center}
\end{frame}

@@

		\item Each read may be used in forward or reverse-complement
		orientation, depending on the orientation of the arrow head when the
		corresponding vertex is entered.
	\end{itemize}
	\begin{figure}[H]
		{\small
		\begin{tikzpicture}[>=triangle 45]
			\tikzstyle{every node} = [circle,fill=blue!20,draw=black];
			\node (1) at (0.00, 0) {1};
			\node (2) at (1.75, 0) {2};
			\node (3) at (3.50, 0) {3};
			\node (4) at (5.25, 0) {4};
			\draw[<->,very thick] (1) edge (2);
			\draw[>-<,very thick] (2) edge (3);
			\draw[<-<,very thick] (3) edge (4);
		\end{tikzpicture} }

@@

		\begin{tikzpicture}
				\draw[<-,style=very thick] (0.0, 0.0) -- (3.0, 0.0);
				\draw[<-,style=very thick] (0.8, -0.3) -- (3.8, -0.3);
				\draw[->,style=very thick] (1.6, -0.6) -- (4.6, -0.6);
				\draw[<-,style=very thick] (2.4, -0.9) -- (5.4, -0.9);
				\draw (-0.3, 0.0) node {1.};
				\draw (-0.3, -0.3) node {2.};
				\draw (-0.3, -0.6) node {3.};
				\draw (-0.3, -0.9) node {4.};
		\end{tikzpicture}
		\caption{A bidirected graph and the implied assembly of the
		corresponding reads}
	\end{figure}
\end{frame}

@@

		\begin{center}
			\begin{tikzpicture}
				\draw[->,style=very thick] (0,0) node[anchor=east] {f} -- (2,0);
				\draw[->,style=very thick] (0.5,0.25) node[anchor=east] {g} -- (2.5,0.25);
				\draw[->,style=very thick] (1.0,0.5) node[anchor=east] {h} -- (3,0.5);
			\end{tikzpicture}
			\begin{tikzpicture}[>=triangle 45]
				\tikzstyle{every node} = [circle,fill=blue!20,draw=black];
				\node (f) at (0, 0) {f};
				\node (g) at (1.5, 0) {g};
				\node (h) at (3, 0) {h};
				\draw[>->,style=very thick] (f) edge (g);
				\draw[>->,style=very thick] (g) edge (h);
				\draw[>->,style=very thick,bend left] (f) edge (h);
			\end{tikzpicture}
		\end{center}

		\item Walks visiting more vertices are preferred because they are
		supported by more reads, and the overlaps tend to be longer.  So, we
		would like to throw away \BidirectedEdgeForward{$f$}{$h$} but keep
		\BidirectedEdgeForward{$f$}{$g$} and \BidirectedEdgeForward{$g$}{$h$}.

@@

\begin{frame}{Transitive reduction (cont.)}
		Transitive reduction algorithm:  Go through each vertex and examine
		neighbors up to 2 steps away to identify all transitive edges leaving this
		vertex.
	\begin{algorithm}[H]
		\caption{{\sc TransitiveReduction}($G$)}
	{\footnotesize
		\begin{algorithmic}
			\FOR{{\bf each} vertex $v \in G$}
				\STATE{Mark all neighbors of $v$ as {\tt INPLAY}.}
				\STATE{Set {\tt longest} $\gets$ length of the longest edge leaving $v$}
				\FOR{{\bf each} edge $v \to w$ in order of length}
					\FOR{{\bf each} edge $w \to x$ in order of length}
						\IF{$x$ is not marked {\tt INPLAY}}
							\STATE{\bf continue}
						\ENDIF
						\IF{$len(v \to w) + len(w \to x) > $ {\tt longest}}
							\STATE{\bf break}
						\ENDIF
						\STATE{Mark $x$ as {\tt ELIMINATED}}
					\ENDFOR
				\ENDFOR
				\STATE{Mark as transitive all edges $v \to x$ where $x$ is marked {\tt ELIMINATED}}
			\ENDFOR
			\STATE{Eliminate all edges marked transitive.}
		\end{algorithmic}
	}
	\end{algorithm}
\end{frame}

>>>>

\newcommand{\ReadArrowType}{latex}

\newcommand{\LengthVar}{L}

@@

\begin{frame}[fragile]{Details of assembler input}
	\begin{itemize}
		\item The reads given to an assembler (my code, as well as most
		other assemblers) as input can be in a simple plain-text format:
	\end{itemize}
	\begin{verbatim}
	>read_1
	AAATCGGCGCGTAAACAGGCAGCCAGCACCGCAGCA
	>read_2
	GAGTAGTCGGAACCGTTGCGTCCAAGCATTAGTGTA
	>read_3
	TAGCGGCCAGGATGCTTTACCCAATATCAGCGATGC
	...
	\end{verbatim}
	\begin{itemize}
		\item The assembler may use other DNA sequence representations
		(e.g. a binary representation with 2 bits per base) internally.
	\end{itemize}
\end{frame}

\begin{frame}[fragile]{Details of assembler output}
	\begin{itemize}
		\item Most assemblers can generate output in the same plain-text
		format.
		\item A {\bf contig} is a continuous sequence of DNA that was
		assembled.  Ideally, each contig should be much longer than the
		original reads.
	\end{itemize}
	\begin{verbatim}
	>contig_1
	GTTGCGAGATTTGGACGGACGTTGACGGGGTCTATACCTGCGACCCGCGTCA
	GGTGCCCGATGCGAGGTTGTTGAAGTCGATGTCCTACCAGGAAGCGATGGAG
	CTTTCCTACTTCGGCGCTAAAGTTCTTCACCCCCGCACCATTACCCCCATCG
	CCCAGTTCCAGATCCCTTGCCTGATTAAAAATACCGGAAATCCTCAAGCACC
	AGGTACGCTCATTGGTGCCAGCCGTGATGAAGACGAATTACCGGTCAAGGGC
	ATTTCCAATCTGAATAACATGGCAATGTTCAGCGTTTCTGGTCCGGGGATGA
	...
	\end{verbatim}
\end{frame}

@@

\begin{frame}{Overlaps between reads}
	Consider two reads, $f$ and $g$, and their reverse-complements $f'$ and $g'$.
	The reads $f$ and $g$ are said to {\bf exactly overlap} by some length
	$\LengthVar$ iff at least one of the following is true:
	\begin{itemize}
		\item The last $\LengthVar$ bp of $f$ exactly match the first
		$\LengthVar$ bp of $g$.
		\item The last $\LengthVar$ bp of $f$ exactly match the first
		$\LengthVar$ bp of $g'$.
		\item The last $\LengthVar$ bp of $f'$ exactly match the first
		$\LengthVar$ bp of $g$.
		\item The last $\LengthVar$ bp of $f'$ exactly match the first
		$\LengthVar$ bp of $g'$.
	\end{itemize}
	An exact overlap $o$ is fully described by the tuple $(f, g, f_{beg},
	g_{beg}, len, rc)$.
	%there $f$ and $g$ are the reads of the overlap,
	%$f_{beg}$ and $g_{beg}$ and the starting position of the overlap on each
	%read, $len$ is the length of the overlap, and $rc$ indicates whether the
	%overlap is reverse-complement or not.
\end{frame}

@@

\begin{frame}{Three types of overlaps}
	\begin{enumerate}
		\item ``Normal'' overlap
			\begin{center}
				\vspace{-0.5cm}
				\begin{tikzpicture}[>=\ReadArrowType]
					\draw[->,style=thick] (0,0) -- (2,0);
					\draw[->,style=thick] (1.0,0.3) -- (3.0,0.3);
				\end{tikzpicture}

@@

				\begin{tikzpicture}[>=\ReadArrowType]
					\draw[->,style=thick] (2,0) -- (0,0);
					\draw[->,style=thick] (3.0,0.3) -- (1.0,0.3);
				\end{tikzpicture}
			\end{center}
		\vspace{0.5cm}
		\item ``Innie'' overlap
			\begin{center}
				\vspace{-0.5cm}
				\begin{tikzpicture}[>=\ReadArrowType]
					\draw[->,style=thick] (0,0) -- (2,0);
					\draw[->,style=thick] (3,0.3) -- (1,0.3);
			\end{tikzpicture} \end{center}
		\vspace{0.5cm}
		\item ``Outie'' overlap
			\begin{center}
			\vspace{-0.5cm}
			\begin{tikzpicture}[>=\ReadArrowType]
					\draw[->,style=thick] (2,0) -- (0,0);
					\draw[->,style=thick] (1.0,0.3) -- (3.0,0.3);
			\end{tikzpicture} \end{center}
	\end{enumerate}
\end{frame}

\begin{frame}{Computing overlaps}
	\begin{itemize}
		\item Goal: compute all pairwise overlaps of some minimum length
		$\LengthVar$ among the reads.
		\item Naive algorithm compares every read with every other read ($N$
		reads: $N^2$ time)
		\item A faster algorithm indexes the reads by short subsequences, then
		only compares reads that share a subsequence
		(``seed-and-extend'').
		\item Overlaps may be exact, or they may allow for differences up to a
		certain threshold.
	\end{itemize}
\end{frame}

\begin{frame}{Computing overlaps (Implementation)}
	\begin{itemize}
		\item Implementation: {\tt compute-overlaps}
			\begin{itemize}
				\item {\bf Input}:  A set of reads and the minimum overlap
				length $\LengthVar$
				\item {\bf Output}:  All exact pairwise overlaps between reads,
				including reverse-complement overlaps
				\item {\bf Algorithm}:  Seed-and-extend
				\item {\bf Running time}: Linear with respect to genome length
				for non-repetitive genomes; quadratic with respect to read
					density; quadratic with respect to the number of times a
					sequence of DNA is repeated in the genome
			\end{itemize}
	\end{itemize}
	%\begin{algorithm}[H]
		%\caption{Algorithm {\sc compute-overlaps}($S$)}
		%\begin{algorithmic}
			%%\STATE{h = new hash table}
			%%\FOR{{\bf each} read $r \in S$}
				%%\FOR{{\bf each} canonical $k$-mer $K \in R$}
					%%\STATE{Append $K.pos$ to $h[K]$}
				%%\ENDFOR
			%%\ENDFOR
			%%\FORALL{posList $\in h$}
				%%\FORALL{$k$-mer pairs $k1$, $k2$ in
			%%\ENDFOR
		%\end{algorithmic}
	%\end{algorithm}
\end{frame}

@@

		\begin{center}
			\begin{tikzpicture}[>=\ReadArrowType]
				\draw[->,style=thick] (0,0) -- (2,0);
				\draw[->,style=thick] (3,0.3) -- (1,0.3);
			\end{tikzpicture}
			\hspace{5mm}or\hspace{5mm}
			\begin{tikzpicture}[>=\ReadArrowType]
				\draw[->,style=thick] (0,0.3) -- (2,0.3);
				\draw[->,style=thick] (3, 0) -- (1, 0);
			\end{tikzpicture}
			\hspace{5mm} ?
		\end{center}

@@

		\begin{center}
			\begin{tabular}{p{1cm}cccc}
				{\footnotesize Overlap} &
				\begin{tikzpicture}[scale=0.6,>=\ReadArrowType]
						\draw[->,style=thick] (2,0) -- (0,0);
						\draw[->,style=thick] (1,0.3) -- (3,0.3);
				\end{tikzpicture}
				&
				\begin{tikzpicture}[scale=0.6,>=\ReadArrowType]
						\draw[->,style=thick] (0,0) -- (2,0);
						\draw[->,style=thick] (3,0.3) -- (1,0.3);
				\end{tikzpicture}
				&
				\begin{tikzpicture}[scale=0.6,>=\ReadArrowType]
						\draw[->,style=thick] (0,0) -- (2,0);
						\draw[->,style=thick] (1,0.3) -- (3,0.3);
				\end{tikzpicture}
				&
				\begin{tikzpicture}[scale=0.6,>=\ReadArrowType]
						\draw[->,style=thick] (2,0) -- (0,0);
						\draw[->,style=thick] (3,0.3) -- (1,0.3);
				\end{tikzpicture}
				\\
				&$\downarrow$ & $\downarrow$& $\downarrow$& $\downarrow$ \\
				{\footnotesize Bidirected edge} &
				\begin{tikzpicture}[scale=0.6,>=triangle 45]
						\draw[<->,style=thick] (0,0) -- (2,0);
				\end{tikzpicture}
				&
				\begin{tikzpicture}[scale=0.6,>=triangle 45]
						\draw[>-<,style=thick] (0,0) -- (2,0);
				\end{tikzpicture}
				&
				\begin{tikzpicture}[scale=0.6,>=triangle 45]
						\draw[>->,style=thick] (0,0) -- (2,0);
				\end{tikzpicture}
				&
				\begin{tikzpicture}[scale=0.6,>=triangle 45]
						\draw[<-<,style=thick] (0,0) -- (2,0);
				\end{tikzpicture}
			\end{tabular}
		\end{center}

@@

\begin{frame}{Walks in a bidirected graph}
	\begin{itemize}
		\item A {\bf walk in a bidirected graph} $G$ is a continuous sequence of
		edges in $G$ such that if any vertex $v$ is entered through a head
		inwards, it is left on a head outwards (unless it is the end of the
		path), and vice versa.
		\item A bidirected edge may be traversed in opposite directions during
		the same walk.
		\item The reverse of a walk in a bidirected graph is also a
		valid walk.
		\item $1 \to 2 \to 3 \to 4$ and $4 \to 3 \to 2 \to 1$ are both valid
		walks in the bidirected graph below.
	\end{itemize}
		\begin{center} {\small
		\begin{tikzpicture}[>=triangle 45]
			\tikzstyle{every node} = [circle,fill=blue!20,draw=black];
			\node (1) at (0.00, 0) {1};
			\node (2) at (1.75, 0) {2};
			\node (3) at (3.50, 0) {3};
			\node (4) at (5.25, 0) {4};
			\draw[<->,very thick] (1) edge (2);
			\draw[>-<,very thick] (2) edge (3);
			\draw[<-<,very thick] (3) edge (4);
		\end{tikzpicture} } \end{center}
\end{frame}

@@

		\item Each read may be used in forward or reverse-complement
		orientation, depending on the orientation of the arrow head when the
		corresponding vertex is entered.
	\end{itemize}
	\begin{figure}[H]
		{\small
		\begin{tikzpicture}[>=triangle 45]
			\tikzstyle{every node} = [circle,fill=blue!20,draw=black];
			\node (1) at (0.00, 0) {1};
			\node (2) at (2.0, 0) {2};
			\node (3) at (4.0, 0) {3};
			\node (4) at (6.0, 0) {4};
			\draw[<->,very thick] (1) edge (2);
			\draw[>-<,very thick] (2) edge (3);
			\draw[<-<,very thick] (3) edge (4);
		\end{tikzpicture} }

@@

		\begin{tikzpicture}[>=\ReadArrowType]
				\draw[<-,style=very thick] (0.0, 0.0) -- (4.0, 0.0);
				\draw[<-,style=very thick] (1.2, -0.3) -- (5.2, -0.3);
				\draw[->,style=very thick] (2.4, -0.6) -- (6.4, -0.6);
				\draw[<-,style=very thick] (3.6, -0.9) -- (7.6, -0.9);
				\draw (-0.3, 0.0) node {1.};
				\draw (-0.3, -0.3) node {2.};
				\draw (-0.3, -0.6) node {3.};
				\draw (-0.3, -0.9) node {4.};
		\end{tikzpicture}
		\caption{A bidirected graph and the implied assembly of the
		corresponding reads}
	\end{figure}
\end{frame}

@@

		\begin{center}
			\begin{tikzpicture}
				\draw[->,style=very thick] (0,0) node[anchor=east] {f} -- (2,0);
				\draw[->,style=very thick] (0.6,0.25) node[anchor=east] {g} -- (2.6,0.25);
				\draw[->,style=very thick] (1.2,0.5) node[anchor=east] {h} -- (3.2,0.5);
			\end{tikzpicture}
			\begin{tikzpicture}[>=triangle 45]
				\tikzstyle{every node} = [circle,fill=blue!20,draw=black];
				\node (f) at (0, 0) {f};
				\node (g) at (1.7, 0) {g};
				\node (h) at (3.4, 0) {h};
				\draw[>->,style=very thick] (f) edge (g);
				\draw[>->,style=very thick] (g) edge (h);
				\draw[>->,style=very thick,bend left] (f) edge (h);
			\end{tikzpicture}
		\end{center}

		\item Walks visiting more vertices are preferred because they are
		supported by more reads and the overlaps tend to be longer.  So, we
		would like to throw away \BidirectedEdgeForward{$f$}{$h$} but keep
		\BidirectedEdgeForward{$f$}{$g$} and \BidirectedEdgeForward{$g$}{$h$}.

@@

\begin{frame}{Transitive reduction (cont.)}
		Transitive reduction algorithm:  Go through each vertex $v$ and
		examine vertices up to 2 edges away from $v$ to identify all
		transitive edges leaving $v$.
	\begin{algorithm}[H]
		\caption{{\sc TransitiveReduction}($G$)}
	{\footnotesize
		\begin{algorithmic}
			\FOR{{\bf each} vertex $v \in G$}
				\STATE{Mark all neighbors of $v$ as {\tt INPLAY}}
				\STATE{Set {\tt longest} $\gets$ length of the longest edge leaving $v$}
				\FOR{{\bf each} edge $v \to w$ in order of length}
					\FOR{{\bf each} edge $w \to x$ in order of length}
						\IF{$x$ is not marked {\tt INPLAY}}
							\STATE{\bf continue}
						\ENDIF
						\IF{$len(v \to w) + len(w \to x) > $ {\tt longest}}
							\STATE{\bf break}
						\ENDIF
						\STATE{Mark $x$ as {\tt ELIMINATED}}
					\ENDFOR
				\ENDFOR
				\STATE{Mark as transitive all edges $v \to x$ where $x$ is marked {\tt ELIMINATED}}
			\ENDFOR
			\STATE{Eliminate all edges marked transitive}
		\end{algorithmic}
	}
	\end{algorithm}
\end{frame}
